---
title: "Characterising multicomponent biodiversity change"
author: "Shane Blowes"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
<!-- badges: end -->

This repository includes R code to reproduce the analyses shown in the article: 

**Local biodiversity change reflects interactions among changing abundance, evenness and richness**

*by Shane A. Blowes, Gergana N. Daskalova, Maria Dornelas, Thore Engel, Nicholas J. Gotelli, Anne Magurran, Inês S. Martins, Brian McGill, Daniel J. McGlinn, Alban Sagouis, Hideyasu Shimadzu, Sarah R. Supp, and Jonathan M. Chase*

Here we give a brief overview on the code and data files in this repository.

## Data

Files in the data folder include:

**conceptual_communities.Rdata**: simulated data to reproduce Figure 1.

**conceptual_figure_dat.Rdata**: simulated data to reproduce Figure 2.

**long_table.csv**: data for *Temporal comparisons: experimental or natural perturbations*. This data is was prepared for analysis by Alban Sagouis, using code available here: https://github.com/chase-lab/BioTIMEx

**PREDICTS_alpha.Rdata**: data for *Spatial comparison: anthropogenic perturbations*; this is the output of 01_PREDICTS_data_wrangle.R 

**spatial_natural.Rdata**: data for *Spatial comparison: natural environmental variation*; this is the output of 01a_CESTES_mcgill_combine.R


## Code 
Files in the r_scripts folder include

00_: script to load packages and set working directory

01_: scripts to prepare data for analyses. BioTIME data were prepared using code available here: https://github.com/sChange-workshop/BioGeo-BioDiv-Change. Perturbed time series data were compiled and standardised with code written by Alban Sagouis available here: https://github.com/chase-lab/BioTIMEx 

02_: scripts to fit models to the data. Some were written to run on a scientific computing cluster.

03_: script to do posterior predictive checks.

04_: scripts to wrangle posteriors for plotting results.

05_: scripts to present results: figures and supplemental table.

200_: script to generate data for conceptual figure.

## Results
Files in the results folder include:

**bt_multi4_pois3_lnorm_results.Rdata**: output of 04_bt_multi4_posterior_wrangle.R

**btx_multi4_global_results.Rdata**: output of 04_btx_global_multi4_posterior_wrangle.R

**predicts_multi4_results.Rdata**: output of 04_PREDICTS_multi_coef_wrangle.R

**spatial_multi4_results.Rdata**: output of 04_spat_natural_multi4_posterior_wrangle.R


---
title: "BioTIMEx"
author: "Alban Sagouis"
date: "7/22/2020"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## BioTIMEx

### Description
This research compendium regroups scripts used to download, re-structure and aggregate data sets to constitute a large meta-analysis of communities in experimental setups sampled several times.
The code found here was originally versionned using git and stored on github <>, and was eventually submitted to Zenodo <>. This code accompanies the article: XXXXX.

### Reproducibility and R environment
To ensure that the working environment (R version and package version) are documented and isolated, the package renv (<https://rstudio.github.io/renv/index.html>) was used. By running `renv::restore()`, renv will install all missing packages at once. This function will use the `renv.lock` file to download the same versions of packages that we used.

### Methods
Data sets were originally searched for among LTER data sets and suitable open access data stored on EPI were selected (<https://portal.edirepository.org/nis/home.jsp>).

Suitable data sets were individually downloaded from R. Scripts managing these downloads are grouped inside `R/data download/`. These scripts follow EDI process of data checking and formatting. You can run all these scripts at once by running this command here or from `R/1.0_downloading_raw_data.r`:

```{r eval=FALSE}
if(!dir.exists('data/raw data/'))   dir.create('data/raw data/')
listF <- list.files('./R/data download', pattern = ".R|.r", full.names = TRUE)
lapply(listF, function(fullPath) source(fullPath, encoding = 'UTF-8', echo = FALSE, local = TRUE))
```

All downloaded data sets are saved in separate folders named following the convention `author_year`.

In a second step, each data set is re-structured or wrangled to fit a common format before analysis. The scripts turning the original heterogeneously structured data sets into comparable tables are in the `./R/data wrangling/` folder. You can run all these scripts at once by running this command here or from `R/2.0-wrangling_raw_data.r`:

```{r eval=FALSE}
if(!dir.exists('data/wrangled data/'))   dir.create('data/wrangled data/')
listF <- list.files('R/data wrangling', pattern = ".R|.r", full.names = TRUE)
lapply(listF, function(fullPath) source(fullPath, encoding = 'UTF-8', echo = FALSE, local = TRUE))
```

Finally, all restructured tables are aggregated together in a final table by the `.R/3.0_merging_long-format_tables.r` script. The structure of the end-product table is a long format with each row recording the composition of a community in one place at a given time. Format is described in `./data/template long format.txt` and variables are defined.

### Analyses
Further analyses were carried at on R too by Shane Blowes and collaborators.
